Covid-19 infection and attributable mortality in UK long term care facilities: Data quality and methodology report

### 2020-07-21 manuscript_appendix/manuscript_appendix.Rmd
realign dates to manuscript + fix typos

---
title: 'Incidence of confirmed COVID-19 cases in care home staff and residents: Data
  quality and methodology report'
bibliography: ../manuscript/references.bib
output:
  html_document:
    code_folding: hide
    df_print: kable
    keep_md: yes
    toc: yes
    toc_depth: 1
  word_document:
    toc: yes
    toc_depth: 1
    reference_docx: ../manuscript/template.docx
always_allow_html: yes
---

@@

library(summarytools)
st_options(
  headings = FALSE,
  footnote = NA
)
source("../.Rprofile")
devtools::load_all("..")
library(dplyr)
library(ggplot2)
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)
load_data()
date_min <- as.Date("2020-03-02")
date_max <- as.Date("2020-06-07") #as.Date("2020-06-15")
date_min_tallies <- as.Date("2020-03-24")
date_max_tallies = as.Date("2020-06-07")

@@

A total of `r desc_before_exclusions$nrow_incidents` incident reports were obtained. Resident pseudoidentifiers were absent in `r formatbm(desc_before_exclusions$missing_id)` (`r tbrounding(desc_before_exclusions$missing_id_pct)`%) of Datix incident reports. The pseudoidentifiers of a further `r desc_before_exclusions$link_fail ` reports (`r tbrounding(desc_before_exclusions$link_fail /desc_before_exclusions$nrow_incidents*100)`%) were could not be successfully linked to the residents database. All were excluded, leaving a total of `r nrow(incidents)` reports dated between `r format(date_min, "%A %e %b %Y")` and  `r format(date_max, "%A %e %b %Y")` relating to `r formatbm(dplyr::n_distinct(incidents$resident_id))` unique residents.
These reports belongued to `r formatbm(dplyr::n_distinct(incidents$home_code))` care homes totalling `r formatbm(sum(beds[beds$year=="2020" & beds$home_code %in% unique(incidents$home_code), "beds"]))` beds. For the period of study, the Four Seasons Health Care Group (FSHCG) comprises `r formatbm(dplyr::n_distinct(beds[beds$year=="2020", "home_code"]))` care homes with a total of `r formatbm(sum(beds[beds$year=="2020", "beds"]))` beds.

>>>>

---
title: "Covid-19 infection and attributable mortality in UK long term care facilities: Data quality and methodology report"
bibliography: ../manuscript/references.bib
output:
  word_document:
    toc: yes
    toc_depth: 1
    reference_docx: ../manuscript/template.docx
  html_document:
    code_folding: hide
    df_print: kable
    keep_md: yes
    toc: yes
    toc_depth: 1
always_allow_html: yes
---

@@

library(summarytools)
st_options(
  headings = FALSE,
  footnote = NA
)
source("../.Rprofile")
devtools::load_all("..")
library(dplyr)
library(ggplot2)
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)
load_data()
date_min <- as.Date("2020-03-02")
date_max <- as.Date("2020-06-14") #as.Date("2020-06-15")
date_min_tallies <- as.Date("2020-03-24")
date_max_tallies = as.Date("2020-06-14")

@@

A total of `r formatbm(desc_before_exclusions$nrow_incidents)` incident reports were obtained. Resident pseudoidentifiers were absent in `r formatbm(desc_before_exclusions$missing_id)` (`r tbrounding(desc_before_exclusions$missing_id_pct)`%) of Datix incident reports. The pseudoidentifiers of a further `r desc_before_exclusions$link_fail ` reports (`r tbrounding(desc_before_exclusions$link_fail /desc_before_exclusions$nrow_incidents*100)`%) were could not be successfully linked to the residents database. All were excluded, leaving a total of `r nrow(incidents)` reports dated between `r format(date_min, "%A %e %B %Y")` and  `r format(date_max, "%A %e %B %Y")` relating to `r formatbm(dplyr::n_distinct(incidents$resident_id))` unique residents.
These reports belonged to `r formatbm(dplyr::n_distinct(incidents$home_code))` care homes totalling `r formatbm(sum(beds[beds$year=="2020" & beds$home_code %in% unique(incidents$home_code), "beds"]))` beds. For the period of study, the Four Seasons Health Care Group (FSHCG) comprises `r formatbm(dplyr::n_distinct(beds[beds$year=="2020", "home_code"]))` care homes with a total of `r formatbm(sum(beds[beds$year=="2020", "beds"]))` beds.
